A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-21 4_method.tex
prove single upward edge property

From any node in the graph which is not a saddle point there is only a single edge going upward.
\todo{Explanation / proof needed.}
%See VoronoiQuadrangulation::filterUnmarkedRegions
This means that walking up the graph from a marked region to a local maximum follows a single path without branchings.

>>>>

From any node in the graph which is not a saddle point there is at most a single edge going upward.
Any branch point $v$ in the VD coincides with the circumcircle of its support $p_1, p_2, p_3$.
If $v$ lies within $\triangle p_1 p_2 p_3$ it is a local maximum and otherwise we will show it has exactly one upward edge.
If $v$ lies outside of $\triangle p_1 p_2 p_3$ then those support points lie within a \SI{180}{\degree} range from $v$
and one point lies in the middle, say $\angle p_1 + \angle p_2 = \angle p_3$.
Then a circle with radius $R(v) + \epsilon$ around $w$ such that $|v-w| < 2 \epsilon$ can only touch $p_1$ and $p_3$.
See \cref{branch_upward_edge_property}.
%See VoronoiQuadrangulation::filterUnmarkedRegions
This means that walking up the graph from a marked region to a local maximum follows a single path without branching.

\begin{figure}
\centering
\includegraphics[width=.4\columnwidth]{sources/method/branch_upward_edge_property.pdf}
\caption{The radial distance can only increase along one edge around a branch point in the VD.}
\label{branch_upward_edge_property}
\end{figure}
